Supplementary material to ``Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data''

### 2015-08-03 scirep_version.tex
deleted appendix from draft_lm1 and updated scirep_version. closes #42

\bibitem{honorio_temporal_2009}
\bibinfo{author}{Hon\'orio, N.~A.}, \bibinfo{author}{Code\c{c}o, C.~T.},
  \bibinfo{author}{Alves, F.~C.}, \bibinfo{author}{Magalh\~aes, M.} \&
  \bibinfo{author}{Louren\c{c}o-De-Oliveira, R.}
\newblock \bibinfo{title}{Temporal distribution of aedes aegypti in different
  districts of rio de janeiro, brazil, measured by two types of traps}.
\newblock \emph{\bibinfo{journal}{Journal of Medical Entomology}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{1001--1014}
  (\bibinfo{year}{2009}).
\newblock \urlprefix\url{http://www.bioone.org/doi/abs/10.1603/033.046.0505}.

@@

@@

\bibitem{macedo_virological_2013}
\bibinfo{author}{Macedo, G.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Virological surveillance for early warning of dengue
  epidemics in the state of rio de janeiro, brazil}.
\newblock \emph{\bibinfo{journal}{Transactions of the Royal Society of Tropical
  Medicine and Hygiene}} \textbf{\bibinfo{volume}{107}},
  \bibinfo{pages}{141--146} (\bibinfo{year}{2013}).

\bibitem{luz_disability_2009}
\bibinfo{author}{Luz, P.~M.}, \bibinfo{author}{Grinsztejn, B.} \&
  \bibinfo{author}{Galvani, A.~P.}
\newblock \bibinfo{title}{Disability adjusted life years lost to dengue in
  brazil}.
\newblock \emph{\bibinfo{journal}{Tropical Medicine \& International Health}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{237--246}
  (\bibinfo{year}{2009}).
\newblock

@@

\bibitem{duarte_data_2006}
\bibinfo{author}{Duarte, H. H.~P.} \& \bibinfo{author}{Fran\c{c}a, E.~B.}
\newblock \bibinfo{title}{Data quality of dengue epidemiological surveillance
  in belo horizonte, southeastern brazil}.
\newblock \emph{\bibinfo{journal}{Revista de Sa\'ude P\'ublica}}
  \textbf{\bibinfo{volume}{40}}, \bibinfo{pages}{134--142}
  (\bibinfo{year}{2006}).
\newblock

@@

\bibitem{mira2001}
\bibinfo{author}{Mira, A.}
\newblock \bibinfo{title}{On metropolis-hastings algorithms with delayed
  rejection}.
\newblock \emph{\bibinfo{journal}{Metron}} \textbf{\bibinfo{volume}{59}},
  \bibinfo{pages}{231--241} (\bibinfo{year}{2001}).

>>>>

\bibitem{honorio_temporal_2009}
\bibinfo{author}{Hon\'orio, N.~A.}, \bibinfo{author}{Code\c{c}o, C.~T.},
  \bibinfo{author}{Alves, F.~C.}, \bibinfo{author}{Magalh\~aes, M.} \&
  \bibinfo{author}{Louren\c{c}o-De-Oliveira, R.}
\newblock \bibinfo{title}{Temporal distribution of aedes aegypti in different
  districts of rio de janeiro, {B}razil, measured by two types of traps}.
\newblock \emph{\bibinfo{journal}{Journal of Medical Entomology}}
  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{1001--1014}
  (\bibinfo{year}{2009}).
\newblock \urlprefix\url{http://www.bioone.org/doi/abs/10.1603/033.046.0505}.

@@

\bibitem{nogueira1999dengue}
\bibinfo{author}{Nogueira, R. M.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Dengue in the state of rio de janeiro, brazil,
  1986-1998}.
\newblock \emph{\bibinfo{journal}{Mem{\'o}rias do Instituto Oswaldo Cruz}}
  \textbf{\bibinfo{volume}{94}}, \bibinfo{pages}{297--304}
  (\bibinfo{year}{1999}).

\bibitem{de2004dengue}
\bibinfo{author}{De~Simone, T.} \emph{et~al.}
\newblock \bibinfo{title}{Dengue virus surveillance: the co-circulation of
  {DENV}-1, {DENV}-2 and {DENV}-3 in the state of {R}io de {J}aneiro,
  {B}razil}.
\newblock \emph{\bibinfo{journal}{Transactions of the Royal Society of Tropical
  Medicine and Hygiene}} \textbf{\bibinfo{volume}{98}},
  \bibinfo{pages}{553--562} (\bibinfo{year}{2004}).

\bibitem{nogueira2011dengue}
\bibinfo{author}{Nogueira, R.~M.} \& \bibinfo{author}{Eppinghaus, A.~L.}
\newblock \bibinfo{title}{Dengue virus type 4 arrives in the state of {R}io de
  {J}aneiro: a challenge for epidemiological surveillance and control}.
\newblock \emph{\bibinfo{journal}{Mem{\'o}rias do Instituto Oswaldo Cruz}}
  \textbf{\bibinfo{volume}{106}}, \bibinfo{pages}{255--256}
  (\bibinfo{year}{2011}).

@@

\bibitem{macedo_virological_2013}
\bibinfo{author}{Macedo, G.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Virological surveillance for early warning of dengue
  epidemics in the state of {R}io de {J}aneiro, {B}razil}.
\newblock \emph{\bibinfo{journal}{Transactions of the Royal Society of Tropical
  Medicine and Hygiene}} \textbf{\bibinfo{volume}{107}},
  \bibinfo{pages}{141--146} (\bibinfo{year}{2013}).

\bibitem{luz_disability_2009}
\bibinfo{author}{Luz, P.~M.}, \bibinfo{author}{Grinsztejn, B.} \&
  \bibinfo{author}{Galvani, A.~P.}
\newblock \bibinfo{title}{Disability adjusted life years lost to dengue in
  {B}razil}.
\newblock \emph{\bibinfo{journal}{Tropical Medicine \& International Health}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{237--246}
  (\bibinfo{year}{2009}).
\newblock

@@

\bibitem{duarte_data_2006}
\bibinfo{author}{Duarte, H. H.~P.} \& \bibinfo{author}{Fran\c{c}a, E.~B.}
\newblock \bibinfo{title}{Data quality of dengue epidemiological surveillance
  in belo horizonte, southeastern {B}razil}.
\newblock \emph{\bibinfo{journal}{Revista de Sa\'ude P\'ublica}}
  \textbf{\bibinfo{volume}{40}}, \bibinfo{pages}{134--142}
  (\bibinfo{year}{2006}).
\newblock

@@

\bibitem{honorio2009spatial}
\bibinfo{author}{Hon{\'o}rio, N.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Spatial evaluation and modeling of dengue
  seroprevalence and vector density in {R}io de {J}aneiro, {B}razil}.
\newblock \emph{\bibinfo{journal}{PLoS Negl Trop Dis}}
  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{e545} (\bibinfo{year}{2009}).
